Project 4

### 2018-11-18 Project4/report/ms.tex

\begin{figure}[t]
\mbox{\epsfig{figure=accepts_of_T-T1T2_4-L20.pdf,width=\linewidth,clip=}}
\caption{Logarithm of the accepted states as a function of the temperature for different }
\label{fig:logAccepts}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=accepts-T1T2_4-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{Description of figure -- explain all elements, but do not
draw conclusions here.}
\label{fig:figure_label}
\end{figure}

>>>>

\begin{figure}[t]
\mbox{\epsfig{figure=accepts_of_T-T1T2_4-L20.pdf,width=\linewidth,clip=}}
\caption{Logarithm of the accepted states as a function of the temperature for different number of Monte Carlo cycles. The left four dots corresponds to $T=1$ kT/J, and the right four dots corresponds to $T=2.4$ kT/J. The initial spins are randomly organized.}
\label{fig:logAccepts(t)}
\end{figure}

\begin{figure}[t]
\mbox{\epsfig{figure=accepts-T1T2_4-L20-1e5.pdf,width=\linewidth,clip=}}
\caption{Logarithmic plot of accepted states as a function of }
\label{fig:logAccepts}
\end{figure}
